Clean spectral data

### 2021-02-25 R/clean_spectral_data.Rmd
print dimensions of spectra since itts cut off from the glimpse command output

```{r, message=TRUE}
message("# of unique individualID values:")
length(unique(all_spectra$individualID))

>>>>

```{r, message=TRUE}
# dimensions of the spectra file 
message("dimensions of all_spectra.csv file: rows   cols")
dim(all_spectra)

message("# of unique individualID values:")
length(unique(all_spectra$individualID))
